NumPy---Array Programming in Python

### 2020-01-26 body.tex
Brief accounting of eht-imaging and pycbc libraries.
Added a few sentences on how components of the scientific
python ecosystem are used by pycbc and eht-imaging for the
analysis of gravitational wave data and black hole imaging,
respectively.

Focused mostly on numpy, scipy, and matplotlib.

>>>>

The \tt{eht-imaging} library developed by the Event Horizon Telescope 
collabortion relies on many components of the scientific Python ecosystem.
NumPy arrays were used to store and manipulate numerical data at every step
in the processing chain: from raw data through calibration and image 
reconstruction.
Scipy was used to provide tools used in general image processing such as 
filtering and image alignment, while scikit\_image provided higher-level
functionality such as edge filters and Hough transforms.
Other components of Scipy are used throughout the library, such as the
\tt{scipy.optimize} package for handling general optimization tasks.
Matplotlib is used for visualizing data throughout the analysis pipeline,
including the generation of the final image of the black hole.
% N.B. - most of this comes from introspecting the Image class defined in
% ehtim/image.py.

Tools for analyzing data from gravitational wave observatories such as LIGO
and Virgo are provided by the \tt{pycbc} package, which was used in the first
detection of gravitationaly waves \cite{abbott2016observation} and in 
on-going analysis of data from LIGO and Virgo.
\tt{pycbc} make extensive use of the scientific Python ecosystem.
The time-series data from the interferometers are stored in NumPy arrays,
while the \tt{scipy.signal} is used to construct and apply filters to the
data.
Matplotlib is used to visualize data at all points along the analysis chain
including raw data from the instrumentation and the time-frequency 
visualization of the ``chirp'' from the binary black hole merger.
